Combinatorial interpretations of holonomic recurrences

### 2021-08-16 article/main.tex
Describe lambda case

\RequirePackage{color}
\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
\definecolor{blue(pigment)}{rgb}{0.2, 0.2, 0.6}
\definecolor{egyptianblue}{rgb}{0.06, 0.2, 0.65}

\RequirePackage{listings}
\lstset{
    basicstyle=\small
}

@@

@@

\[B = \text{leaf} + B^2\]

\todo{Add some image}

@@

iilll\todo{Add image}
\end{example}

@@

\begin{example}
    \(\n \n \no \n \no \no \no\)
    \todo{Add image}
\end{example}

@@

We also created a framework, called transformator, that may help visualize our work. It is based on the idea that every transformation described using bijective language can be translated to a function transforming node and finite number of its surrounding nodes. This function can not discriminate nodes on the grounds of their kind. The only discrimination that may occur may be connected to the following cases:
\begin{itemize}
    \item node has no children, ie.~is a virtual leaf (which corresponds to the size of the tree, \(n\));
    \item node has has children, ie.~is not a virtual leaf (which corresponds to \(n - 1\));
    \item node has its parent on the left, ie.~is right child of its parent;
    \item node has its parent on the right, ie.~is left child of its parent.
\end{itemize}

@@

\[\begin{array}{rccrlc}
        S_{0,0} &=& (& (k + 1) C_k,& \emptyset &)\\
        S_{1,0} &=& (& - (2 k + 1) C_k,& \{l\} &)\\
        S_{1,1} &=& (& - 2 (k + 1) C_k,& \{s\} &)\\
        S_{2,0} &=& (& - (4 k) C_k,& \{aou\} &)\\
        S_{2,1} &=& (& (k) C_k,& \{ll\} &)\\
        S_{2,2} &=& (& (4 k + 2) C_k,& \{ls\} &)\\
        S_{2,3} &=& (& (k + 1) C_k,& \{ss\} &)\\
        S_{3,0} &=& (& 2 (2 k + 1) C_k,& \{aosu\} &)\\
        S_{3,1} &=& (& - (2 k) C_k,& \{lls\} &)\\
        S_{3,2} &=& (& - (2 k + 1) C_k,& \{lss\} &)\\
        S_{4,0} &=& (& k C_k,& \{llss\} &)\\
\end{array}\]

@@

\begin{lstlisting}
=== Classes stats ===
[ ]  0,0:       0 of      16 | (k + 1) * Ck              []
[ ]  1,0:       0 of     -10 | - (2 * k + 1) * Ck        [l]
[ ]  1,1:       0 of     -12 | - 2 * (k + 1) * Ck        [s]
[ ]  2,0:       0 of      -4 | - (4 * k) * Ck            [aou]
[ ]  2,1:       0 of       1 | (k) * Ck                  [ll]
[ ]  2,2:       0 of       6 | (4 * k + 2) * Ck          [ls]
[ ]  2,3:       0 of       2 | (k + 1) * Ck              [ss]
[ ]  3,0:       0 of       2 | 2 * (2 * k + 1) * Ck      [aosu]
[x]  3,1:       0 of       0 | - (2 * k) * Ck            [lls]
[ ]  3,2:       0 of      -1 | - (2 * k + 1) * Ck        [lss]
[x]  4,0:       0 of       0 | k * Ck                    [llss]
\end{lstlisting}

@@

\begin{lstlisting}
# define 0,0: (k + 1) * Ck []
=== Classes stats ===
[x]  0,0:      16 of      16 | (k + 1) * Ck              []
[ ]  1,0:       0 of     -10 | - (2 * k + 1) * Ck        [l]
[ ]  1,1:       0 of     -12 | - 2 * (k + 1) * Ck        [s]
[ ]  2,0:       0 of      -4 | - (4 * k) * Ck            [aou]
[ ]  2,1:       0 of       1 | (k) * Ck                  [ll]
[ ]  2,2:       0 of       6 | (4 * k + 2) * Ck          [ls]
[ ]  2,3:       0 of       2 | (k + 1) * Ck              [ss]
[ ]  3,0:       0 of       2 | 2 * (2 * k + 1) * Ck      [aosu]
[x]  3,1:       0 of       0 | - (2 * k) * Ck            [lls]
[ ]  3,2:       0 of      -1 | - (2 * k + 1) * Ck        [lss]
[x]  4,0:       0 of       0 | k * Ck                    [llss]
=== Diff stats ===
0,0:     0    16
\end{lstlisting}

@@

\includeinlinesvg{.19}{trees_00__4_base.svg}%
\(\Rightarrow\)
\includeinlinesvg{.19}{trees_00__4.svg}%
\includeinlinesvg{.19}{trees_00__5.svg}%
\includeinlinesvg{.19}{trees_00__6.svg}%
\includeinlinesvg{.19}{trees_00__7.svg}%

@@

\includeinlinesvg{.33}{trees_00__2.svg}%
\includeinlinesvg{.33}{trees_00__3.svg}%
\includeinlinesvg{.33}{trees_00__7.svg}%

\includeinlinesvg{.33}{trees_00__4.svg}%
\includeinlinesvg{.33}{trees_00__12.svg}%
\includeinlinesvg{.33}{trees_00__13.svg}%

\includeinlinesvg{.20}{trees_00__0.svg}%
\includeinlinesvg{.20}{trees_00__1.svg}%
\includeinlinesvg{.20}{trees_00__5.svg}%
\includeinlinesvg{.20}{trees_00__6.svg}%
\includeinlinesvg{.20}{trees_00__8.svg}%

\includeinlinesvg{.20}{trees_00__9.svg}%
\includeinlinesvg{.20}{trees_00__10.svg}%
\includeinlinesvg{.20}{trees_00__11.svg}%
\includeinlinesvg{.20}{trees_00__14.svg}%
\includeinlinesvg{.20}{trees_00__15.svg}%

@@

\includeinlinesvg{.24}{trees_100__0_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__0.svg}%
\includeinlinesvg{.24}{trees_100__1_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__1.svg}%

\includeinlinesvg{.24}{trees_100__2_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__2.svg}%
\includeinlinesvg{.24}{trees_100__3_base.svg}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__3.svg}%

@@

@@

You may ask how we achieved such partial result.

@@

\todo{finish interpretation}
\todo{missing formal proof}

>>>>

\RequirePackage{color}
\definecolor{ao(english)}{rgb}{0.0, 0.5, 0.0}
\definecolor{blue(pigment)}{rgb}{0.2, 0.2, 0.6}
\definecolor{egyptianblue}{rgb}{0.06, 0.2, 0.65}
\definecolor{lightgray}{gray}{0.60}

\RequirePackage{listings}
\lstset{
    basicstyle=\footnotesize\ttfamily,
    comment=[l]{\#},
    morecomment=[s]{/*}{*/},
    commentstyle=\color{lightgray}\ttfamily,
    escapeinside={<@}{@>}
}

@@

Green edges 
\begin{minipage}{1.5em}
\includesvg[width=\textwidth]{green_edge}
\end{minipage}
depict edges to \(\no\) nodes.

@@

\begin{center}
    \begin{minipage}[t]{.2\textwidth}
        \begin{center}
            \(B\)\\
            \includesvg[scale=0.5]{binary_tree_def_1}%
        \end{center}
    \end{minipage}%
    \begin{minipage}[t]{.05\textwidth}
        \begin{center}
            \(=\)\\
        \end{center}
    \end{minipage}%
    \begin{minipage}[t]{.2\textwidth}
        \begin{center}
            \(\text{leaf}\)\\
            \includesvg[scale=0.5]{binary_tree_def_2}%
        \end{center}
    \end{minipage}%
    \begin{minipage}[t]{.05\textwidth}
        \begin{center}
            \(+\)\\
        \end{center}
    \end{minipage}%
    \begin{minipage}[t]{.2\textwidth}
        \begin{center}
            \(B^2\)\\
            \includesvg[scale=0.5]{binary_tree_def_3}%
        \end{center}
    \end{minipage}%
\end{center}

@@

\begin{center}
    \includesvg[scale=.7]{iilll}
\end{center}
\end{example}

@@

\begin{example}
    \(\n \n \no \n \no \no \no\)
    \begin{center}
        \includesvg[scale=.7]{oononnn}
    \end{center}
\end{example}

@@

We also created a framework, called transformator, that may help visualize our work. It is based on the idea that every transformation described using bijective language can be translated to a function transforming node and finite number of its surrounding nodes. This function can not discriminate nodes on the grounds of their kind. The only discrimination that may occur may be connected to the following cases:
\begin{itemize}
    \item node has no children, ie.~is a virtual leaf (which corresponds to the size of the tree, \(n\));
    \item node has has children, ie.~is not a virtual leaf (which corresponds to \(n - 1\));
    \item node is a root (which corresponds to \(1\));
    \item node has its parent on the left, ie.~is right child of its parent;
    \item node has its parent on the right, ie.~is left child of its parent.
\end{itemize}

@@

\[\begin{array}{rccrlc}
        S_{0,0} &=& (& (k + 1) C_k,& \emptyset &)\\
        S_{1,0} &=& (& - (2 k + 1) C_k,& \{l\} &)\\
        S_{1,1} &=& (& - 2 (k + 1) C_k,& \{s\} &)\\
        S_{2,0} &=& (& - (4 k) C_k,& \{ao\} &)\\
        S_{2,1} &=& (& (k) C_k,& \{ll\} &)\\
        S_{2,2} &=& (& (4 k + 2) C_k,& \{ls\} &)\\
        S_{2,3} &=& (& (k + 1) C_k,& \{ss\} &)\\
        S_{3,0} &=& (& 2 (2 k + 1) C_k,& \{aos\} &)\\
        S_{3,1} &=& (& - (2 k) C_k,& \{lls\} &)\\
        S_{3,2} &=& (& - (2 k + 1) C_k,& \{lss\} &)\\
        S_{4,0} &=& (& k C_k,& \{llss\} &)\\
\end{array}\]

@@

\begin{lstlisting}
=== Classes stats ===
[ ]  0,0:       0 of      16 | (k + 1) * Ck              []
[ ]  1,0:       0 of     -10 | - (2 * k + 1) * Ck        [l]
[ ]  1,1:       0 of     -12 | - 2 * (k + 1) * Ck        [s]
[ ]  2,0:       0 of      -4 | - (4 * k) * Ck            [ao]
[ ]  2,1:       0 of       1 | (k) * Ck                  [ll]
[ ]  2,2:       0 of       6 | (4 * k + 2) * Ck          [ls]
[ ]  2,3:       0 of       2 | (k + 1) * Ck              [ss]
[ ]  3,0:       0 of       2 | 2 * (2 * k + 1) * Ck      [aos]
[x]  3,1:       0 of       0 | - (2 * k) * Ck            [lls]
[ ]  3,2:       0 of      -1 | - (2 * k + 1) * Ck        [lss]
[x]  4,0:       0 of       0 | k * Ck                    [llss]
\end{lstlisting}

@@

\begin{lstlisting}
# define 0,0: (k + 1) * Ck []
=== Classes stats ===
[x]  0,0:      16 of      16 | (k + 1) * Ck              []
[ ]  1,0:       0 of     -10 | - (2 * k + 1) * Ck        [l]
[ ]  1,1:       0 of     -12 | - 2 * (k + 1) * Ck        [s]
[ ]  2,0:       0 of      -4 | - (4 * k) * Ck            [ao]
[ ]  2,1:       0 of       1 | (k) * Ck                  [ll]
[ ]  2,2:       0 of       6 | (4 * k + 2) * Ck          [ls]
[ ]  2,3:       0 of       2 | (k + 1) * Ck              [ss]
[ ]  3,0:       0 of       2 | 2 * (2 * k + 1) * Ck      [aos]
[x]  3,1:       0 of       0 | - (2 * k) * Ck            [lls]
[ ]  3,2:       0 of      -1 | - (2 * k + 1) * Ck        [lss]
[x]  4,0:       0 of       0 | k * Ck                    [llss]
=== Diff stats ===
0,0:     0    16
\end{lstlisting}

@@

\includeinlinesvg{.19}{trees_00__4_base}%
\(\Rightarrow\)
\includeinlinesvg{.19}{trees_00__4}%
\includeinlinesvg{.19}{trees_00__5}%
\includeinlinesvg{.19}{trees_00__6}%
\includeinlinesvg{.19}{trees_00__7}%

@@

\includeinlinesvg{.33}{trees_00__2}%
\includeinlinesvg{.33}{trees_00__3}%
\includeinlinesvg{.33}{trees_00__7}%

\includeinlinesvg{.33}{trees_00__4}%
\includeinlinesvg{.33}{trees_00__12}%
\includeinlinesvg{.33}{trees_00__13}%

\includeinlinesvg{.16}{trees_00__0}%
\includeinlinesvg{.16}{trees_00__1}%
\includeinlinesvg{.16}{trees_00__5}%
\includeinlinesvg{.16}{trees_00__6}%
\includeinlinesvg{.16}{trees_00__14}%
\includeinlinesvg{.16}{trees_00__15}%

\includeinlinesvg{.25}{trees_00__8}%
\includeinlinesvg{.25}{trees_00__9}%
\includeinlinesvg{.25}{trees_00__10}%
\includeinlinesvg{.25}{trees_00__11}%

@@

\includeinlinesvg{.24}{trees_100__0_base}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__0}%
\includeinlinesvg{.24}{trees_100__1_base}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__1}%

\includeinlinesvg{.24}{trees_100__2_base}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__2}%
\includeinlinesvg{.24}{trees_100__3_base}\(\Rightarrow\)\includeinlinesvg{.24}{trees_100__3}%

@@

Next, we can take care of the later cases of section \(0, 0\). It can be also expressed using sections \(1, 0\) and \(1, 1\):

# old visitior
c.append_r_class_subtree_visitor(-1,
    lambda kind, left, right:
        None if kind[0] is None else
        ["l", kind] + left + right + [(None, "*")]
)

# new visitior
c.append_r_class_right_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["l", parent_kind] + [left[0] + ("*",)] + left[1:] + right + [None]
)

# new visitior
c.append_r_class_left_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["l", parent_kind] + left + [right[0] + ("*",)] + right[1:] + [None]
)

c.define_section(1)

# old visitior
c.append_r_class_right_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", (None, "*"), parent_kind] + left + right
)

# new visitior
c.append_r_class_left_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, parent_kind] + left + [right[0] + ("*",)] + right[1:]
)

# new visitior
c.append_r_class_right_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, parent_kind] + [left[0] + ("*",)] + left[1:] + right
)
\end{lstlisting}

Basicaly, for each virtual node not being root (ie.\ having left or right parent), we point it and add \(l\) or \(s\) respectively above the parent.

\includeinlinesvg{.32}{trees_111__1_base}%
\(\Rightarrow\)
\includeinlinesvg{.32}{trees_101__0}%
\includeinlinesvg{.32}{trees_112__0}%

The last row can be generated using section \(2, 0\):

\begin{lstlisting}
c.define_class(2)

c.append_r_class_subtree_visitor(-1,
    lambda kind, left, right:
        None if kind[0] is None else
        ["a", "o", (None, "*"), None, kind] + left + right
)

c.append_r_class_subtree_visitor(-1,
    lambda kind, left, right:
        None if kind[0] is None else
        ["a", "o", None, (None, "*"), kind] + left + right
)

c.append_r_class_subtree_visitor(-1,
    lambda kind, left, right:
        None if kind[0] is None else
        ["a", kind] + left + right + ["o", (None, "*"), None]
)

c.append_r_class_subtree_visitor(-1,
    lambda kind, left, right:
        None if kind[0] is None else
        ["a", kind] + left + right + ["o", None, (None, "*")]
)
\end{lstlisting}

For each actual vertex, we add \(a\) node as its left or right parent and add as a second child \(o\) node as its siblig. We then point left or right virtual child of newly created \(o\) node.

\includeinlinesvg{.20}{trees_200__0_base}%
\(\Rightarrow\)
\includeinlinesvg{.20}{trees_200__0}%
\includeinlinesvg{.20}{trees_201__0}%
\includeinlinesvg{.20}{trees_202__0}%
\includeinlinesvg{.20}{trees_203__0}%

After such transformations, we get following statistics:

\begin{lstlisting}
=== Classes stats ===
[x]  0,0:      16 of      16 | (k + 1) * Ck              []
[x]  1,0:     -10 of     -10 | - (2 * k + 1) * Ck        [l]
[ ]  1,1:      -9 of     -12 | - 2 * (k + 1) * Ck        [s]
[x]  2,0:      -4 of      -4 | - (4 * k) * Ck            [ao]
[ ]  2,1:       0 of       1 | (k) * Ck                  [ll]
[ ]  2,2:       0 of       6 | (4 * k + 2) * Ck          [ls]
[ ]  2,3:       0 of       2 | (k + 1) * Ck              [ss]
[ ]  3,0:       0 of       2 | 2 * (2 * k + 1) * Ck      [aos]
[x]  3,1:       0 of       0 | - (2 * k) * Ck            [lls]
[ ]  3,2:       0 of      -1 | - (2 * k + 1) * Ck        [lss]
[x]  4,0:       0 of       0 | k * Ck                    [llss]
=== Diff stats ===
1,0:     4     0
1,1:     3     0
\end{lstlisting}

This construction works also for bigger \(N\):

\begin{lstlisting}
=== Classes stats ===
[x]  0,0:   39050 of   39050 | (k + 1) * Ck              []
[x]  1,0:  -23237 of  -23237 | - (2 * k + 1) * Ck        [l]
[ ]  1,1:  -17799 of  -24460 | - 2 * (k + 1) * Ck        [s]
[x]  2,0:  -13728 of  -13728 | - (4 * k) * Ck            [ao]
[ ]  2,1:       0 of    3432 | (k) * Ck                  [ll]
[ ]  2,2:       0 of   14586 | (4 * k + 2) * Ck          [ls]
[ ]  2,3:       0 of    3861 | (k + 1) * Ck              [ss]
[ ]  3,0:       0 of    4620 | 2 * (2 * k + 1) * Ck      [aos]
[ ]  3,1:       0 of   -2156 | - (2 * k) * Ck            [lls]
[ ]  3,2:       0 of   -2310 | - (2 * k + 1) * Ck        [lss]
[ ]  4,0:       0 of     342 | k * Ck                    [llss]
=== Diff stats ===
1,0:  7602     0
1,1:  5832     0
2,0:  2280     0
\end{lstlisting}

The process can then be repeated for each section. We have chosen lexicographical order (ie. \(0,0\); \(1,0\); \(1,1\); \(2,0\); \(\ldots\)).

\subsection{Final result}%
\label{sub:final_result}

After multiple iterations, we managed to come up with following construction:

c.append_r_class_subtree_visitor(1,
    lambda kind, left, right:
        None if kind[0] is not None else
        [kind + ("*", )] + left + right
)

c.define_class(1)

c.append_r_class_subtree_visitor(-1,
    lambda kind, left, right:
        None if kind[0] is None else
        ["l", kind] + left + right + [(None, "*")]
)

c.append_r_class_right_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["l", parent_kind] + [left[0] + ("*",)] + left[1:] + right + [None]
)

c.append_r_class_left_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["l", parent_kind] + left + [right[0] + ("*",)] + right[1:] + [None]
)

c.define_section(1)

c.append_r_class_right_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", (None, "*"), parent_kind] + left + right
)

c.append_r_class_left_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, parent_kind] + left + [right[0] + ("*",)] + right[1:]
)

c.append_r_class_right_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, parent_kind] + [left[0] + ("*",)] + left[1:] + right
)

c.define_class(2)

c.append_r_class_subtree_visitor(-1,
    lambda kind, left, right:
        None if kind[0] is None else
        ["a", "o", (None, "*"), None, kind] + left + right
)

c.append_r_class_subtree_visitor(-1,
    lambda kind, left, right:
        None if kind[0] is None else
        ["a", "o", None, (None, "*"), kind] + left + right
)

c.append_r_class_subtree_visitor(-1,
    lambda kind, left, right:
        None if kind[0] is None else
        ["a", kind] + left + right + ["o", (None, "*"), None]
)

c.append_r_class_subtree_visitor(-1,
    lambda kind, left, right:
        None if kind[0] is None else
        ["a", kind] + left + right + ["o", None, (None, "*")]
)

c.define_section(1)

c.append_r_class_subtree_visitor(1,
    lambda kind, left, right:
        None if kind[0] is None else
        ["l", "l", kind] + left + right + [(None, "*"), None]
)

c.define_section(2)

c.append_r_class_right_parent_subtree_visitor(1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["l", "s", (None, "*"), parent_kind] + left + right + [None]
)

c.append_r_class_subtree_visitor(1,
    lambda kind, left, right:
        None if kind[0] is None else
        ["s", None, "l", kind] + left + right + [(None, "*")]
)

c.append_r_class_right_parent_subtree_visitor(1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, "l", parent_kind] + left + right + [(None, "*")]
)

c.append_r_class_right_parent_subtree_visitor(1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, "l", parent_kind] + [left[0] + ("*", )] + left[1:] + right + [None]
)

c.append_r_class_left_parent_subtree_visitor(1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, "l", parent_kind] + left + [right[0] + ("*", )] + right[1:] + [None]
)

c.define_section(3)

c.append_r_class_right_parent_subtree_visitor(1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, "s", (None, "*"), parent_kind] + left + right
)

c.define_class(3)

c.append_r_class_right_parent_subtree_visitor(1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, "a", "o", (None, "*"), None, parent_kind] + left + right
)

c.append_r_class_right_parent_subtree_visitor(1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, "a", "o", None, (None, "*"), parent_kind] + left + right
)

c.append_r_class_right_parent_subtree_visitor(1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, "a", parent_kind] + left + right + ["o", (None, "*"), None]
)

c.append_r_class_right_parent_subtree_visitor(1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, "a", parent_kind] + left + right + ["o", None, (None, "*")]
)

c.define_section(1)

c.append_r_class_right_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, "l", "l", parent_kind] + left + right + [(None, "*"), None]
)

c.append_r_class_right_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        ["s", None, "l", "l", parent_kind] + left + right + [(None, "*"), None]
)

c.define_section(2)

c.append_r_class_right_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, "s", None, "l", parent_kind] + left + right + [(None, "*")]
)

c.append_r_class_right_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, "l", "s", (None, "*"), parent_kind] + left + right + [None]
)

c.define_class(4)

c.append_r_class_right_parent_subtree_visitor(1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, "s", None, "l", "l", parent_kind] + left + right + [(None, "*"), None]
)
\end{lstlisting}

It resulted in final statistics:

\begin{lstlisting}
=== Classes stats ===
[x]  0,0:   39050 of   39050 | (k + 1) * Ck              []
[x]  1,0:  -23237 of  -23237 | - (2 * k + 1) * Ck        [l]
[ ]  1,1:  -17799 of  -24460 | - 2 * (k + 1) * Ck        [s]
[x]  2,0:  -13728 of  -13728 | - (4 * k) * Ck            [ao]
[x]  2,1:    3432 of    3432 | (k) * Ck                  [ll]
[ ]  2,2:   10833 of   14586 | (4 * k + 2) * Ck          [ls]
[ ]  2,3:    1770 of    3861 | (k + 1) * Ck              [ss]
[ ]  3,0:    2280 of    4620 | 2 * (2 * k + 1) * Ck      [aos]
[ ]  3,1:   -1648 of   -2156 | - (2 * k) * Ck            [lls]
[ ]  3,2:   -1140 of   -2310 | - (2 * k + 1) * Ck        [lss]
[ ]  4,0:     187 of     342 | k * Ck                    [llss]
=== Diff stats ===
\end{lstlisting}

As you can see, diff stats are empty, so we managed to generate expected trees on both sides of the equation.

You may also note that we didn't generate all trees suggested by the recurrence. This is due to one cheat we used.

@@

You may remember our assumptions in section \ref{sub:the_framework} about the discrimination cases. We allowed ourselves to apply visitors only to one of left and right child, which isn't handled by our holonomic recurrence as number of such vertices do not depend only on \(n\).

To fix this, one can for example add construction for section \(1, 0\) to generate all expected trees from it and then repeat the iteration in order to generate matching trees on the other side of the equation. We can see that we used \(2\) constructions visiting node with right parent and only one visiting node having left parent, so our missing construction should also visit nodes with left parent.

c.append_r_class_right_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", (None, "*"), parent_kind] + left + right
)

c.append_r_class_left_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, parent_kind] + left + [right[0] + ("*",)] + right[1:]
)

c.append_r_class_right_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", None, parent_kind] + [left[0] + ("*",)] + left[1:] + right
)

# example missing construction
c.append_r_class_left_parent_subtree_visitor(-1,
    lambda kind, parent_kind, left, right:
        None if kind[0] is not None else
        ["s", (None, "*"), parent_kind] + left + right
)
\end{lstlisting}

Please note that it is only an example of missing construction. It is just the simplest one we could think about, and in that case, simple solution is most often the correct one.

@@

First thing to be done, that comes to mind immediately, is to finish the construction eliminating the cheat mentioned in section \ref{sub:the_cheat}.

You may also note that we are operating on specific \(N\). The probability that we miss some corner case is low, but even if we check large \(N\) values, it is always present. The formal algebraic proof would make us sure that the construction works. We woulr prioritize finishing the construction first.

The framework also isn't perfect. It highly depends on the operator's intuition. We believe that the solving process can be automated. The simplest method that comes to mind is simply creating heuristic rules that then will be used by the framework to guess at least partial solution.

We believe that one day all of that will be done.
